---
title: "Association Rules Practice"
author: "Dennis Tseng, 2018/06/23"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(showtext)
showtext_auto()
font_add("jh", "msjh.ttc")
```

### Conclusion

This project is my trial to apply association rules to the real-world data. There are many precious tutorials and one of them not only talk about abstract concepts but also practical application of `arules` package in R. [The article](https://cran.r-project.org/web/packages/arules/vignettes/arules.pdf) is on CRAN. Besides, I use data from [here](https://github.com/nupur1492/RProjects/blob/master/MarketBasketAnalysis/groceries.csv). The data is bundled with a tutorial, though there are many mistakes in that article. Thus, I give up and try to understand and practice association rulses on my own. Hope it works!

```{r message = F, warning = F}
library(tidyverse)
library(arules)
library(arulesViz)
library(knitr)
library(kableExtra)
rm(list=ls())
df <- read_csv("D:/R_programming/DSprogramming/groceries.csv",
               col_types = cols(
                 Member_number = col_character(),
                 Date = col_date("%m/%d/%Y"),
                 itemDescription = col_character()))
names(df) <- c("member_ID", "date", "item")
```

Let's take a look at the data!

```{r message = F, warning = F}
glimpse(df)
```

There are three columns of this grocery data, which are member_ID, date, and items bought. Each observation contains an item only, so if a customer buy 5 items in the same time, it will account for 5 observations. Now I am goint to use `group_by` to check the real number of transaction.

```{r message = F, warning = F}
df %>% group_by(member_ID, date) %>%
  count(sort = T)
```

`arules` needs a primary key, but primary key in `df` is composite key. I convert it below. `group_id` is the new single primary key of `df2`. We can take a look at ```glimpse(df2)``` and ```df2 %>% group_by(group_id) %>% count(sort = T) %>% glimpse()```

```{r message = F, warning = F}
df2 <- df %>%
  unite(gawy, c(member_ID, date), sep = "-")
df2$group_id <- df2 %>% group_indices(gawy)
df2$gawy <- NULL
df2 <- df2 %>% select(group_id, item) %>% arrange(group_id)
glimpse(df2)
df2 %>% group_by(group_id) %>% count(sort = T) %>% glimpse()
```

After completing the transformation of df2, it is needed to use function in `arules` to continue.

```{r message = F, warning = F}
#write.csv(df2, "df2.csv") I have wrriten it.
order_trans <- read.transactions(
  file = "df2.csv",
  format = "single",
  sep = ",",
  cols=c("group_id","item"),
  rm.duplicates = T
)
length(order_trans)
dim(order_trans)
size(order_trans)
image(order_trans)
summary(order_trans)
```

`order_trans` is a specific data type in `arules` package. It is a sparse matrix consists of transactions as row and items as columns. If items appear in a transcation, the value will be 1, and 0 vice versa. ```size(order_trans)``` indicates items bought in each transcation. ```image(order_trans)``` gives us a broader look to the big picture. It is useful to check the condition such as whether some items are out of shelter.

```{r message = F, warning = F}
itemFrequencyPlot(order_trans, topN=10,type="absolute")
```

We can take a look at the frequency plot. It is clear that whole milk is a hot item. So are rolls/buns.

```{r message = F, warning = F}
basket_rules <- apriori(order_trans, parameter = list(sup = 0.01, conf = 0.5,target="rules"))
rules <- sort(basket_rules, decreasing = TRUE, by = "confidence")
```

`apriori` is one of algorithm of association rules. Using `apriori` function, `order_trans` are transformed into `rules`, another specific data type related to association rules. Let's take a look at it.

```{r message = F, warning = F}
inspect(rules)
summary(rules)
```

`rules` tell about the basic concept underling association rules. We can also check that in the plot form.

```{r rules = F, warning = F}
plot(basket_rules)
plot(rules, method = "grouped", control = list(k = 5))
plot(rules, method = "graph", control = list(type = "items"))
plot(rules, method = "paracoord",  control = list(alpha = .5, reorder = TRUE))
```

To conclude, I applied the concepts learned and tried many useful packages such as `dplyr`, `arules` in this porject. I spent much time in understanding association rules and application in real life. I wish I could hand the real world data next time!


