---
title: "HW3"
author: "Dennis Tseng"
date: "2018/3/17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### This is the 7.5.1.1 exercise from chapter 7 **Exploratory Data Analysis** in [The art of R programming](http://diytranscriptomics.com/Reading/files/The%20Art%20of%20R%20Programming.pdf).

#### The question is "Use what you¡¦ve learned to improve the visualisation of the departure times of cancelled vs. non-cancelled flights."

```{r , message = FALSE, results = FALSE}
library(tidyverse)
library(nycflights13)
data(flights)
str(flights)

# arr_time = NA means that the flight was cancelled
# add cancelled column to identify
flights_cancellation <- flights %>%
  mutate(cancelled = is.na(arr_time))
```

#### Now I am going to plot the result. There are several options I can choose to plot.
#### Before plotting, we have to know the type of variables, which are "cancelled" and "dep_time" in this case.

```{r , message = FALSE, warning = FALSE}
head(flights_cancellation$cancelled)
head(flights_cancellation$dep_time)
```

#### Now we know that "cancelled" is a categorical variable and "dep_time" is a continuous variable.
#### Les's plot!

```{r , message = FALSE, warning = FALSE}
# plot01
# draw the plot00
flights_cancellation %>%
  ggplot(aes(x = cancelled)) +
  geom_bar()
```

#### It is quite clear that there is counts gap within flights.

```{r , message = FALSE, warning = FALSE}
# plot01
flights_cancellation %>%
  ggplot(aes(x = dep_time)) +
  geom_freqpoly(aes(col = cancelled), binwidth = 50)
```

#### As you can see, since the counts of cancelled flights are largely less than not-cancelled flights, we can't observe the trend of cancelled flights. Thus, we should change from  ```geom_freqpoly()``` to ```geom_density()```.

```{r , message = FALSE, warning = FALSE}
# plot02
flights_cancellation %>%
  ggplot(aes(x = dep_time)) +
  geom_density(aes(col = cancelled), bw = 40) 
```

#### As you can see, there are some pattern between cancelled and not-cancelled flights.

```{r , message = FALSE, warning = FALSE}
# dplot03
flights_cancellation %>%
  ggplot(aes(x = dep_time)) +
  geom_freqpoly(binwidth = 50) +
  facet_grid( . ~ cancelled)
```

#### Let's add ```facet_grid()``` to the plot, but we need to remember to adjust the geom function.

```{r , message = FALSE, warning = FALSE}
# plot04
flights_cancellation %>%
  ggplot(aes(x = dep_time)) +
  geom_density(bw = 40) +
  facet_grid( . ~ cancelled)
```

#### As you can see, ```facet_grid()``` looks great.

```{r , message = FALSE, warning = FALSE}
# plot05
flights_cancellation %>%
  ggplot(aes(x = cancelled, y = dep_time)) +
  geom_boxplot() 
```

#### As you can see, ```geom_boxplot()``` is also great.

#### To sum up, we use ```geom_freqpoly```, ```geom_density``` and ```geom_boxplot()``` to plot two variables which are "cancelled" and "dep_time". Since there are counts gap, we have to use density to replace counts. Boxplot is also useful to compare continuous variable broken down by a categorical variable.
